Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
adds model predictions to Fig4 (analysis)

		{\footnotesize

@@

@@

				\\ 

@@

				& teddy bear, \textit{bear}, dog, \textit{toy}, stuffed animal, blanket, toys

@@

	\caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames. 

@@

	Second row: top name prediction by bottom up, names which match a MN respose are in italics.}

>>>>

		{\scriptsize

@@

				\rowcolor{lightgray}

@@

@@

				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys

@@

	\caption{Examples for instances of \vgenome synsets with low and high agreement in ManyNames. 

@@

	Second row (gray): top name prediction by bottom up, names which match a MN response are in italics.}
